### 2019-05-07 manuscript.rmd
minor fixes

Different models generating the observed data distribution given the phylogeny were fitted for each continuous character using the function fitContinuous [@harmon2007geiger]. The models compared were the white noise (WN) (non-phylogenetic), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ohnstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory],[@butler2004phylogenetic]. Models were ranked in order of increasing parametric complexity (WN,BM,EB,OU). Corrected Akaika Information Criterion support scores [@sugiura1978further] were compared to the lowest (best) score, and a cutoff of 2 units was used to determine significantly better support. If the best fitting model is not significantly better than a less complex alternative, the least complex model is selected. The models selected for each character were evaluated in terms of model adequacy using the package arbutus [@pennell2015model]. Multivariate BM and OU models were also evaluated using the package mvSLOUCH [@bartoszek2012phylogenetic].

@@

#Combination of VARS and GC sources
diet_VARS = rbind(diet, c(0,0,0,0,0,1,1,0,0))
diet_VARS = cbind(diet_VARS, rep(0,nrow(diet_VARS)))
rownames(diet_VARS)[nrow(diet_VARS)] <- "Lychnagalma utricularia"
names(diet_VARS)[ncol(diet_VARS)] <- "Gelatinous diet"
diet_VARS["Nanomia sp",] = c(1,0,0,0,0,1,1,1,0,1)
diet_VARS["Praya dubia",] = c(1,0,0,0,0,1,1,0,0,1)

@@

#Desmoneme/Rhopaloneme vs crustacean
dprunedCat = binary[which(rownames(binary)%in% rownames(diet)),]
CH_I = dprunedCat$Rhopalonemes
names(CH_I) = rownames(dprunedCat)
CH_J = diet$`Crustacean diet`
names(CH_J) = rownames(diet)
CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
CH_I = CH_I[which(names(CH_I)%in%names(CH_J))]
treeIJ = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_J))))
CH_I = CH_I[match(treeIJ$tip.label, names(CH_I))]
CH_J = CH_J[match(treeIJ$tip.label, names(CH_J))]
fitPagel(treeIJ, CH_I, CH_J)

@@

>>>>

Different models generating the observed data distribution given the phylogeny were fitted for each continuous character using the function fitContinuous [@harmon2007geiger]. The models compared were the white noise (WN) (non-phylogenetic), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ohnstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory],[@butler2004phylogenetic]. Models were ranked in order of increasing parametric complexity (WN,BM,EB,OU). Corrected Akaika Information Criterion support scores [@sugiura1978further] were compared to the lowest (best) score, and a cutoff of 2 units was used to determine significantly better support. If the best fitting model is not significantly better than a less complex alternative, the least complex model is selected. The models selected for each character were evaluated in terms of model adequacy using the package arbutus [@pennell2015model].

@@

#Combination of VARS and GC sources
# diet_VARS = rbind(diet, c(0,0,0,0,0,1,1,0,0))
# diet_VARS = cbind(diet_VARS, rep(0,nrow(diet_VARS)))
# rownames(diet_VARS)[nrow(diet_VARS)] <- "Lychnagalma utricularia"
# names(diet_VARS)[ncol(diet_VARS)] <- "Gelatinous diet"
# diet_VARS["Nanomia sp",] = c(1,0,0,0,0,1,1,1,0,1)
# diet_VARS["Praya dubia",] = c(1,0,0,0,0,1,1,0,0,1)

@@

#Desmoneme/Rhopaloneme vs crustacean
dprunedCat = binary[which(rownames(binary)%in% rownames(diet)),]
CH_I = dprunedCat$Rhopalonemes #same result with desmonemes
names(CH_I) = rownames(dprunedCat)
CH_J = diet$`Crustacean diet`
names(CH_J) = rownames(diet)
CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
CH_I = CH_I[which(names(CH_I)%in%names(CH_J))]
treeIJ = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_J))))
CH_I = CH_I[match(treeIJ$tip.label, names(CH_I))]
CH_J = CH_J[match(treeIJ$tip.label, names(CH_J))]
fitPagel(treeIJ, CH_I, CH_J)

@@

```{r rphylopars_and_varpart}
library(Rphylopars)
combinedata = data.frame(sharedmean_logs,diet[match(sharedmean_logs$Species, rownames(diet)),])
names(combinedata)[1]<-"species"
is.nan.data.frame <- function(x)
do.call(cbind, lapply(x, is.nan))
combinedata[is.nan.data.frame(combinedata)] <- NA
#PhyloParsALL = phylopars(combinedata[,c(1,2,4:22,24,27:42)], ultram, pheno_error = F, pheno_correlated = T)
#PhyloParsALL = phylopars(combinedata[,c(1,32:42)], ultram, pheno_error = F, pheno_correlated = T)

#How to make combined imputations

###PCOA variance partitionaing method
phylomatrix = pcoa(cophenetic(dprunedTree))$vectors
phylomatrix = phylomatrix[match(rownames(diet), rownames(phylomatrix)),]
nastozeroes = dprunedmatrix_logs
nastozeroes[is.nan(dprunedmatrix_logs)]<-0
nastozeroes = nastozeroes[,match(rownames(diet), nastozeroes$Species)]
dietdist <- vegdist(diet, "bray") %>% as.matrix()
varpart(nastozeroes[,-1], phylomatrix[,1:3], diet)
glmatrix_1 = cbind(nastozeroes, phylomatrix)
glmatrix_2 = cbind(nastozeroes, diet)
glmatrix_3 = cbind(nastozeroes, diet, phylomatrix)
glm(Cnidoband.length..um.~Axis.1+Axis.2+Axis.3+Axis.4+Axis.6+Axis.8+Axis.9+Axis.11+Axis.14, data=glmatrix_1[-1,]) -> GLM_1
1-(GLM_1$deviance/GLM_1$null.deviance)
predict.glm(GLM_1, newdata = as.data.frame(glmatrix_1[1,]), se.fit = T)
glm(Cnidoband.length..um.~`Copepod diet`+`Fish diet`+`Amphipod diet`+`Decapod diet`+`Polychaete diet`+`Mollusc diet`+`Crustacean diet`+`Chaetognath diet`+`Ostracod diet`+`Gelatinous diet`, data=glmatrix_2[-1,]) -> GLM_2
1-(GLM_2$deviance/GLM_2$null.deviance)
predict.glm(GLM_2, newdata = as.data.frame(glmatrix_2[1,]), se.fit = T)
glm(Cnidoband.length..um.~Axis.1+Axis.2+Axis.3+Axis.4+Axis.6+Axis.8+Axis.9+Axis.11+Axis.14+`Copepod diet`+`Fish diet`+`Amphipod diet`+`Decapod diet`+`Polychaete diet`+`Mollusc diet`+`Crustacean diet`+`Chaetognath diet`+`Ostracod diet`+`Gelatinous diet`, data=glmatrix_3[-1,]) -> GLM_3
1-(GLM_2$deviance/GLM_2$null.deviance)
predict.glm(GLM_3, newdata = as.data.frame(glmatrix_3[1,]), se.fit = T)

varpart(nastozeroes$coiledness, phylomatrix[,c(1:4,6,8,9,11,14)], diet)
rda(nastozeroes$coiledness, phylomatrix[,c(1:4,6,8,9,11,14)]) %>% summary()

###Phylopars methods
pparsmatrix = cbind(nastozeroes$Species, nastozeroes$Cnidoband.length..um., diet)
names(pparsmatrix)[1]<-"species"
pparsmatrix$`nastozeroes$Cnidoband.length..um.` [1]<-NA
PhyloParsALL = phylopars(pparsmatrix, dprunedTree, pheno_error = F, pheno_correlated = T)
PhyloParsALL$anc_recon["Agalma elegans",]
pparscontrol = pparsmatrix[,1:2]
PhyloPars_control = phylopars(pparscontrol, dprunedTree, pheno_error = F, pheno_correlated = T)
PhyloPars_control$anc_recon["Agalma elegans",]

###PGLS predictions do not take into account the phylogenetic position of the new taxon###
pglsmatrix = glmatrix_2
names(pglsmatrix) = str_replace_all(names(pglsmatrix)," ", "_")
rownames(pglsmatrix) = pglsmatrix$Species
pglm_1 = gls(Cnidoband.length..um. ~ Copepod_diet+Fish_diet+Amphipod_diet+Decapod_diet+Polychaete_diet+Mollusc_diet+Crustacean_diet+Chaetognath_diet+Ostracod_diet+Gelatinous_diet, data=pglsmatrix[,-1], correlation = corBrownian(phy=dprunedTree))
pglm_control = gls(Cnidoband.length..um. ~ Copepod_diet+Fish_diet+Amphipod_diet+Decapod_diet+Polychaete_diet+Mollusc_diet+Crustacean_diet+Chaetognath_diet+Ostracod_diet+Gelatinous_diet, data=pglsmatrix[,-1], correlation = corBrownian(phy=rtree(length(dprunedTree$tip.label))))
predict(pglm_1, newdata = pglsmatrix[1,])
predict(pglm_control, newdata = pglsmatrix[1,])
```
